---
format:
  pdf:
    tbl-cap-location: top
    dpi: 500
    fig-pos: "H"
    number-sections: true
    cite-method: natbib
    include-in-header: 
      - text: |
          \usepackage{lscape}
          \newcommand{\blandscape}{\begin{landscape}}
          \newcommand{\elandscape}{\end{landscape}}
          \usepackage{rotating}
          \newcommand{\bsideways}{\begin{sidewaystable}[htbp]}
          \newcommand{\esideways}{\end{sidewaystable}}
      - file: preamble.tex 
    include-before-body: title.tex
    keep-tex: TRUE
    fig-format: png
    default-image-extension: png
  docx:
    reference-doc: new_template_no_numbering.docx
pdf-engine: lualatex
# monofont: "DejaVu Sans Mono"
# mainfont: "Times New Roman"
execute: 
  echo: false
  warning: false
editor: source
bibliography: references.bib
biblio-style: apalike
natbiboptions: round
link-citations: true
linkcolor: blue!000!black
urlcolor: blue!000!black
citecolor: blue!000!black
linestretch: 1.5
indent: TRUE
title-block-banner: false
title-block-style: none
---

```{r setup}
#| include=FALSE
options(scipen=999)
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE, 
                      dpi = 500, 
                      fig.pos = "H", 
                      fig.env= 'figure', 
                      tab.topcaption = TRUE,
                      ft.align = "left",
                      ft.arraystretch = 0.5,
                      fig.height = 4,
                      fig.width = 7
                      )
library(tidyverse)
library(readr)
library(readxl)
library(zoo)
library(magick)
library(stringi)
library(patchwork)
library(xtable)
library(scales)
library(rvest)
library(rebus)
library(PNWColors)
library(lubridate)
library(here)
library(flextable)
library(gt)
library(officer)
library(officedown)
library(modelsummary)
library(sandwich)
library(lmtest)

set_flextable_defaults(
  font.size = 7,
  digits = 2,
  font.family = "Arial",
  border.color = "black",
  border.width = 0.5,
  fp_border = fp_border(color = "black", width = 0.5, style = "solid")
)


```

```{r functions}
source(here("Functions","flextable_word.R" ))
source(here("Functions","modelsummary_word.R" ))
source(here("Functions","modelplot_word.R" ))
source(here("Functions","borderlines.R" ))
```

# Introduction

According to @bernanke1995, the credit channel is one of the key monetary policy transmission channels. Monetary policy affects the credit channel through its impact on the external finance premium \footnote{The external finance premium is governed by credit-market frictions which cause departures from lenders expected return and potential borrowers’ expected costs.}. Two linkages underscore monetary policy impacts on this premium: the balance sheet and the bank lending channel. The balance sheet channel stems from dynamics in the balance sheet and the incomes of borrowers, while the lending channel deals with how interest rates could impact lenders’ loan supply volumes [@hall2001]. The balance sheet channel has been well established as a significant monetary policy transmission channel [@aysun2013; @altavilla2024; @ashcraft2007]. Notwithstanding, there remains room to provide empirical estimations of the credit channel’s strength due to recent developments in the identification of monetary policy shocks. This is especially true for emerging economies where this work is scant [@pirozhkova2025]. This paper hones in on the balance sheet channel by estimating how climate shocks can reduce (or indeed enhance) the effectiveness of unanticipated monetary policy decisions on the behaviour of borrowers. 

The main motivation of this paper is that like monetary policy shocks, climate shocks – because of their impacts on capital and labour inputs and, in turn, their erosion of firm profitability – can cause frictions within the credit market and have consequential financial stability ramifications [@dafermos2018; @aglietta2016]. In so doing, climate shocks could widen the external finance premium and, in turn, stymie the efficacy of monetary policy pass-through. While this seems a likely course, there is also the potential for monetary policy to mute the deleterious climate shock effects on the credit market, in line with the literature that that studies how monetary policy can be used as a tool to tackle climate change [@roy2024; @monasterolo2018]. In either case, climate shocks play a role in the functioning of the credit market and, consequently, the credit market monetary transmission channel. 

I will investigate to what extent the manifestation of climate shocks act as a credit market friction and how this (potential) friction impacts monetary policy transmission. This involves three parts. First, I will compute the monetary policy shock variable. Second, I will estimate the causal relationships of interest in this work using a panel regression. Finally, I will use a quantile regression procedure to nuance these results.

Only physical shocks, not transition


# Literature review

# Data and methodology

## Data

The analysis draws on three main data sources: climate shocks, monetary policy shocks, and credit extension data. The sample covers South Africa over the period 2011–2025. All series are observed at a quarterly frequency, determined by the availability of the monetary policy shock data; higher-frequency series are aggregated to quarterly values by taking averages or sums where appropriate.

**Climate data:** Temperature and precipitation data are sourced from the ERA5 reanalysis dataset produced by the European Centre for Medium-Range Weather Forecasts. ERA5 provides globally gridded, hourly atmospheric estimates at a 31 km horizontal resolution. Grid-level values are weighted by population and aggregated to monthly averages over South Africa's land area, from which we construct climate shock variables that capture deviations from long-run historical norms in temperature and precipitation.

The climate shocks are calculated as follows:

$$ W_{t} =  \dfrac{T_{t} -\overline{T}_{t} }{\sigma(T_{t})}, $$ {#eq-weather_shock}

where $W_{t}$ is the temperature or precipitation shock at time $t$ and $T_{t}$ is the observed population-weighted climate variable. For both temperature and precipitation, $\overline{T}_{t}$ is the calendar-month mean computed over the full sample period (e.g., the mean of all January values from 2011 to 2025), and $\sigma(T_{t})$ is the corresponding within-month standard deviation. The resulting shock series are shown in @fig-climate_shocks_data in the Appendix.

**Monetary policy data:** The monetary policy shock series is constructed using high-frequency policy surprises for South Africa from @pirozhkova2025, alongside the repurchase (repo) rate from the South African Reserve Bank (SARB). The high-frequency surprises serve as an instrument to purge the endogenous component of policy rate changes, yielding a shock series that satisfies the exogeneity requirement of the regression framework described in @sec-methodology. For robustness, we consider both market-based shocks from @pirozhkova2025 (see @fig-market_based_surprises_data) and a theory-based shock derived from the policy rate, as described in @sec-methodology below (see @fig-theory_based_surprises_data). Surprises are timed to coincide with policy rate announcement dates and aggregated to a quarterly frequency.

**Credit extension data:** Private sector credit extension data — disaggregated by borrower type (households and corporates) at the bank level — are obtained from the SARB's BA900 and BA930 bank compliance reports.^[BA930 data at the bank level are not publicly available.] These series include both credit volumes and lending rates, and are constructed following @sibande2025 and @sibande2025a by sorting and aggregating individual bank records into the broad credit categories used in the study: unsecured, secured, and mortgage credit. Summary charts are provided in @fig-lending_volume_growth_data and @fig-lending_rates.

## Methodology {#sec-methodology}

We use a monetary policy shock, rather than the monetary policy rate itself, as an indicator for monetary policy to ensure exogeneity within the regression framework (Miyajima, 2024). To this end, I replicate a shock variable devised by Merrino (2021) for the South African case based on a simplification of the work of Romer and Romer (2004) as follows:

$$
\Delta r_t = \alpha + \tilde{r_t} + \sum_{t=0}^{2} \beta_t \Delta \tilde{y_t} + \sum_{t=0}^{2} \delta_t \tilde{\pi_t} + \varepsilon_t,
$$ {#eq-mp-shock}

where $\Delta r_t$ is the change in the forecast of the repurchase rate, $\tilde{r_t}$ is the forecasted repo rate in levels, $\tilde{y_t}$ is the forecasted real GDP growth rate, and $\tilde{\pi_t}$ is the forecasted consumer price index inflation rate. The residuals from @eq-mp-shock, $\varepsilon_t$, are used as the $\text{MPShock}_{t}$ explanatory variable that follows in the panel regression estimation. We use a panel regression to primarily test whether monetary policy shocks, when augmented with climate shocks, yield heightened or muted impacts on the credit market as follows:

$$
\text{Credit}_{i,t} = \beta_0 + \beta_1 \text{Climate}_{t}^k  + \beta_2 \text{MPShock}_t + 
\beta_3 (\text{Climate}_t^k \times \text{MPShock}_t) + \Gamma X_t + \gamma_s + \delta_t + \varepsilon_{i,t}, 
$$ {#eq-credit}

where $\text{Credit}_{i,t}$ is the growth rate of credit extended to agent $(s)$ (households or corporates) at time $(t)$, $\text{Climate}_{t}^k$ is the climate shock variable, including temperature and precipitation shocks, as well as extreme wet and dry events, which are each denoted by $k$. The $\text{Climate}_{t}^k\times\text{MPShock}_t$ term tests whether the frictions introduced by climate change shocks are significant enough to modify the pass-through of monetary policy through the credit channel. $X_t$ is a vector of control variables that includes GDP growth, the US Dollar-Rand exchange rate, the loan-to-deposit ratio and the unemployment rate. $\gamma_s$ are agent, time-invariant fixed effects, $\delta_t$ are time fixed effects, and  $\varepsilon_{i,t}$ is the error term.


- robustness specification
- local projections specification


# Results


# Drivers

## Timing sensivity

## Sectoral sensitivity

## Type of shock

# Conclusion

\newpage 

# References {.unnumbered}
::: {#refs}
:::


\setcounter{section}{0}
\renewcommand{\thesection}{\Alph{section}}

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}

\setcounter{figure}{0}
\renewcommand{\thefigure}{A\arabic{figure}}

\newpage

# Appendix

## Data


```{r}
#| label: fig-lending_volume_growth_data
#| fig-cap: "Lending volume growth over time"
#| fig-height: 7
#
lending_volume_growth_gg <- 
  read_rds(here("Outputs", "artifacts_lending_volume.rds")) |> 
  pluck(3)

lending_volume_growth_gg
```


```{r}
#| label: fig-lending_rates
#| fig-cap: "Lending rates overtime"
#| fig-height: 7

lending_rates_gg <- read_rds(here("Outputs", "artifacts_lending_rates.rds")) |> 
  pluck(2)

lending_rates_gg
```


```{r}
#| label: fig-climate_shocks_data
#| fig-cap: Climate Shocks Data
#| fig-height: 2

climate_shocks_gg <- read_rds(here("Outputs", "artifacts_climate_shocks.rds")) |> 
  pluck(2)

climate_shocks_gg
```


```{r}
#| label: fig-market_based_surprises_data
#| fig-cap: "Market-Based Surprises Data"

market_based_surprises_gg <- read_rds(here("Outputs", "artifacts_market_based_surprises.rds")) |> 
  pluck(2)

market_based_surprises_gg
```

```{r}
#| label: fig-theory_based_surprises_data
#| fig-cap: "Theory-based surprises data"
#| fig.height: 2

theory_based_surprises_gg <- read_rds(here("Outputs", "artifacts_surprises.rds")) |> 
  pluck(3, 3)

theory_based_surprises_gg
```


## Descriptive Statistics


```{r}
#| label: tbl-descriptives
#| tbl-cap: "Descriptive statistics"
#| ft.arraystretch: 0.4


descriptives_table <- 
  read_rds(here("Outputs", "artifacts_descriptive_statistics.rds")) |> 
  pluck(1) |>
   mutate(
    credit_category = str_replace_all(credit_category, "pop", "Population"),
    credit_category = str_replace_all(credit_category, "temp", "Temperature"),
    credit_category = str_replace_all(credit_category, "precip", "Precipitation")
  ) |>
  filter(!str_detect(credit_category, "value")) |> 
  mutate(group = factor(
    case_when(
      credit_category %in% c(
        "central_bank_information", "forward_guidance",
        "miyajima_surprise", "romer_surprise", "target",
        "country_risk"
      ) ~ "Monetary Policy",
      str_starts(credit_category, "corporate") ~ "Corporate Credit",
      str_starts(credit_category, "household") ~ "Household Credit",
      str_starts(credit_category, "land_") |
        str_starts(credit_category, "pop_") ~ "Climate"
    ),
    levels = c("Monetary Policy", "Corporate Credit", "Household Credit", "Climate")
  )) |> 
  filter(!str_starts(credit_category, "land_")) |>
  arrange(group, credit_category) |>
  mutate(credit_category = credit_category |> str_replace_all("_", " ") |> str_to_title()) |> 
  as_grouped_data(groups = "group") |>
  flextable() |>
  colformat_double(digits = 2) |>
  set_header_labels(group = "", credit_category = "Variable",
                    mean = "Mean", median = "Median", sd = "SD",
                    min = "Min", max = "Max", n = "N") |>
  width(j = "credit_category", width = 1.5) |>
  width(j = c("mean", "median", "sd", "min", "max"), width = 0.65) |>
  width(j = "n", width = 0.5)
  
descriptives_table

```


## Sector Credit Exposure 

```{r}
#| label: fig-sector_credit_exposure
#| fig-cap: "Sector credit exposure"
#| fig.height: 8


sector_credit_exposure_gg <- 
  read_rds(here("Outputs", "artifacts_sector_credit_exposure.rds")) |> 
  pluck(2)

sector_credit_exposure_gg
```



