---
format:
  pdf:
    tbl-cap-location: top
    dpi: 500
    fig-pos: "H"
    number-sections: true
    cite-method: natbib
    include-in-header: 
      - text: |
          \usepackage{lscape}
          \newcommand{\blandscape}{\begin{landscape}}
          \newcommand{\elandscape}{\end{landscape}}
          \usepackage{rotating}
          \newcommand{\bsideways}{\begin{sidewaystable}[htbp]}
          \newcommand{\esideways}{\end{sidewaystable}}
          \let\oldsection\section
          \renewcommand\section{\oldsection}
      - file: preamble.tex 
    include-before-body: title.tex
    keep-tex: TRUE
    fig-format: png
    default-image-extension: png
  docx:
    reference-doc: new_template_no_numbering.docx
pdf-engine: lualatex
# monofont: "DejaVu Sans Mono"
# mainfont: "Times New Roman"
execute: 
  echo: false
  warning: false
editor: source
bibliography: references.bib
biblio-style: apalike
natbiboptions: round
link-citations: true
linkcolor: blue!000!black
urlcolor: blue!000!black
citecolor: blue!000!black
linestretch: 1.5
indent: TRUE
title-block-banner: false
title-block-style: none
---

```{r setup}
#| include=FALSE
options(scipen=999)
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE, 
                      dpi = 500, 
                      fig.pos = "H", 
                      fig.env= 'figure', 
                      tab.topcaption = TRUE,
                      ft.align = "left",
                      ft.arraystretch = 0.5,
                      fig.height = 4,
                      fig.width = 7
                      )
library(tidyverse)
library(readr)
library(readxl)
library(zoo)
library(magick)
library(stringi)
library(patchwork)
library(xtable)
library(scales)
library(rvest)
library(rebus)
library(PNWColors)
library(lubridate)
library(here)
library(flextable)
library(gt)
library(officer)
library(officedown)
library(modelsummary)
library(sandwich)
library(lmtest)

set_flextable_defaults(
  font.size = 7,
  digits = 2,
  font.family = "Arial",
  border.color = "black",
  border.width = 0.5,
  fp_border = fp_border(color = "black", width = 0.5, style = "solid")
)




```

```{r functions}
source(here("Functions","flextable_word.R" ))
source(here("Functions","modelsummary_word.R" ))
source(here("Functions","modelplot_word.R" ))
source(here("Functions","borderlines.R" ))
```

# Introduction

1. Transmission is not standard as in the models for several reasons eg. info effects. Atheoretical responses to MP exist -- this is what motivated surprise literature. To understand aytipical responses. i.e. there is an unexpected compent to policy -- core issue: MP responses are atheoretical (Kutner, Swansen, Sibande (other paper), Romer and Romer). So we rely... TO BE COMPLETED.

According to @bernanke1995, the credit channel is one of the key monetary policy transmission channels. Monetary policy affects the credit channel through its impact on the external finance premium \footnote{The external finance premium is governed by credit-market frictions which cause departures from lenders expected return and potential borrowers’ expected costs.}. Two linkages underscore monetary policy impacts on this premium: the balance sheet and the bank lending channel. The balance sheet channel stems from dynamics in the balance sheet and the incomes of borrowers, while the lending channel deals with how interest rates could impact lenders’ loan supply volumes [@hall2001]. The balance sheet channel has been well established as a significant monetary policy transmission channel [@aysun2013; @altavilla2024; @ashcraft2007]. Notwithstanding, there remains room to provide empirical estimations of the credit channel’s strength due to recent developments in the identification of monetary policy shocks. This is especially true for emerging economies where this work is scant [@pirozhkova2025]. This paper hones in on the balance sheet channel by estimating how climate shocks can reduce (or indeed enhance) the effectiveness of unanticipated monetary policy decisions on the behaviour of borrowers. 

The main motivation of this paper is that like monetary policy shocks, climate shocks – because of their impacts on capital and labour inputs and, in turn, their erosion of firm profitability – can cause frictions within the credit market and have consequential financial stability ramifications [@dafermos2018; @aglietta2016]. In so doing, climate shocks could widen the external finance premium and, in turn, stymie the efficacy of monetary policy pass-through. While this seems a likely course, there is also the potential for monetary policy to mute the deleterious climate shock effects on the credit market, in line with the literature that that studies how monetary policy can be used as a tool to tackle climate change [@roy2024; @monasterolo2018]. In either case, climate shocks play a role in the functioning of the credit market and, consequently, the credit market monetary transmission channel. 

I will investigate to what extent the manifestation of climate shocks act as a credit market friction and how this (potential) friction impacts monetary policy transmission. 

# Conceptual Framework
We argue that climate shocks may alter the strength of the credit channel by affecting the financial position of corporates, households and banks. For simplicity, we illustrate the transmission of a contractionary monetary policy shock through the credit channel throughout this section. We distinguish between two possible effects that can ensue when a monetary policy shock coincides with a climate shock: amplification and dampening. We define amplification as a strengthening of the response of corporates or households to a monetary policy shock, such that the response of credit rates or volumes moves in the same direction as the response to the monetary policy shock alone, but with a larger absolute magnitude when the climate shock is present. A dampening effect, in contrast, occurs when the response continues to move in the same direction as the response to the monetary policy shock alone, but with a smaller absolute magnitude when the climate shock is present.

## Corporates
From the perspective of corporates, we draw from a framework put forward by @Bean2002Financial as follows:
$$
R_{it}^{c} = R_t + f(D_t/E_t), \qquad f' > 0
$$ {#eq-corporate_interest_rate}

where $R_{it}^{c}$ is the interest rate faced by corporates which is dependent on $R_t$, the risk-free interest rate and a function of the corporate's financial position, in this case represented by its Debt ($D_t$) to Equity ($E_t$) ratio. This function, $f$ therefore represents the external finance premium. Insofar as there are information asymmetries or financial frictions, @eq-corporate_interest_rate holds. 

We posit that climate shocks alter the interest rate faced by corporates through changes in their financial position, which affect the external finance premium and, consequently, the cost of borrowing [@LAUMER2025104949]. In particular, a climate shock can yield supply chain disruptions, damage of capital and production losses. These effects may reduce revenue and profits. Simultaneously, climate shock-related damage may reduce the value of collateral against which corporates borrow. These effects can increase corporate debt, $D_t$, while the associated decline in profitability, asset values and net worth can reduce equity, $E_t$. Consequently, a climate shock may increase a corporate's finance premium and in turn, raise the cost of external finance faced by the corporate. In this way, an adverse climate shock amplifies a contractionary monetary policy shock. 

The same framework allows for a dampening effect of contractionary monetary policy. That is, firms with large cash buffers, liquid assets or adequate insurance coverage may experience little or no deterioration in their balance sheets, resulting in little or no change in $D_t/E_t$ and consequently in the external finance premium, $f(D_t/E_t)$, following a climate shock. This resilience can also render corporates less responsive to the higher borrowing costs. Thus, climate shocks need not strengthen the transmission of monetary policy and may instead leave it unchanged or weaken it. Evidence that cash holdings can mitigate the effect of monetary tightening on corporate investment supports this mechanism [@SharpeSuarez2020].

A final, related potential propagation mechanism for corporates arises from the possibility that corporate borrowing and investment decisions may be relatively less responsive to changes in borrowing costs. If climate shocks demand a need for adaptation, replacement of capital or reconstruction, corporates may have a strong incentive to undertake this investment even when $R_t$ rises. In this case, corporates may become less sensitive to the cost of external finance. This does not necessarily mean that $R_{it}^{c}$ itself falls; rather, the higher financing cost has a smaller effect on corporates' borrowing decisions. This effect would be most evident when higher interest rates coincide with an increase in credit volumes. Consistent with this possibility, @XU2025108087 demonstrate that adaptation policy increases firm investment even in the absence of an easing of financial constraints faced by firms.


## Households

Analogous to @eq-corporate_interest_rate, we this of households facing an interest rate according to the following Equation:
$$
R_{it}^{h} = R_t + \phi_{t}, \qquad \phi_{t} > 0
$$ {#eq-household_interest_rate}
where $R_{it}^{h}$ is the interest rate faced by households as a result of the policy rate $R_t$ and the household-specific spread between the policy rate and the cost of borrowing $\phi_{t}$. The spread can be viewed as reflecting household creditworthiness, indebtedness, income and collateral and other characteristics that affect lenders' assessment of credit risk and the terms at which credit is supplied. Thus, $\phi_{t}$ allows households facing the same monetary policy rate to nevertheless face different borrowing costs. This allowance for differentiated credit market outcomes faced by households is driven by evidence suggesting that transmission of monetary policy varies across households according to a range of factors including their exposure to income fluctuations [@SLACALEK2020103879].

The household mechanism ensues similarly to the case of firms. On the one hand, climate shocks may amplify the credit channel's response to monetary policy shocks. It follows that a climate shock may reduce household income, wealth or damage collateral. This deterioration in the balance sheet of households increases the household-specific spread, $\phi_{t}$, causing affected households to face higher borrowing costs for a given monetary policy rate.  On the other hand, climate shocks may dampen this impact in a similar way to the case of corporates. That is households with liquid assets, insurance coverage or other financial buffers may be able to absorb climate-related losses without a deterioration in their financial position or increased reliance on external finance. In such cases, the climate shock may generate little change in $\phi_{t}$ and therefore need not amplify the response of household borrowing costs to monetary policy.Empirical evidence suggests that insurance may lower debt levels in the face of disasters as households use insurance payouts to pay off mortgages rather than to reconstruct [@Household2017].

## Banks
The household and firm mechanisms are connected through the financial sector. Climate shocks can affect not only borrowers' demand for credit but also banks' willingness to supply it. There is a possibility that during climate shock episodes, creditors heighten the importance they attach to corporates' and households' balance sheet strength. Indeed, there is evidence that mortgage arreas is higher in regions that have faced more damage from climate shocks relative to less damaged regions [@HO2023102790] Recent evidence suggests that in response, banks pose stricter lending conditions to borowers in disaster-prone regions [@Duanmu02012022].

On the other hand, a climate shock may dampen the transmission of monetary policy if it reduces the demand for credit. A deterioration in economic activity following a climate shock or adequate buffers to climate shocks may weaken corporates' and households' demand for new borrowing, reducing banks' loan demand and limiting the extent to which the shock translates into tighter credit conditions. When loan demand is weaker, banks may have less scope or incentive to adjust lending rates in response to changes in the riskiness of their borrowers. In this case, the climate shock may generate little additional increase in the spread between lending rates and the policy rate, thereby limiting its potential to amplify the increase in borrowing costs associated with a monetary policy tightening. 

## Policy 
We must also consider the role that the policy rate, itself, plays in the determination of credit rates and, by extension, volumes. Two related concepts influence our framework. The first is around the mechanics of monetary policy transmission. Monetary policy transmission to lending rates is notoriously heterogeneous across banks and dependent on several factors such as bank balance sheet characteristics [@ALTAVILLA202081].

The second concept relates to the distinction between an anticipated interest rate change and an unanticipated rate change. Monetary policy passthrough in the credit market is faster when the policy rate is correctly anticipated [@KLEIMEIER20061839]. We study monetary policy surprises which, by design, are unanticipated. 

This has non-negligible implications for credit condition outcomes. In particular,...

## Climate Shock Non-Linearity
Until now we have assumed that climate shocks yield adverse effects on corporates, households and banks. This is not necessarily always the case. Consider the case of precipitation shocks. One of the main ways that climate shocks impact macroeconomic outcomes is through the agricultural sector. Agricultural production is reliant on rainfall in the South African context where the majority of crops are rainfed [@Hartley2021ClimateUncertainty] . This dependence is further heightened by the country’s relatively limited water resources [@GovernmentSouthAfrica2024WaterSanitation]. Hence, non-extreme positive precipitation shocks may aid agricultural production. This may, in turn, yield favourable outcomes in the agricultural sector as well as upstream and downstream sectors and ultimately allow for a reduction in $f(D_t/E_t)$ and $\phi_{t}$.

While we present an array of explanations for how climate shocks interact with monetary policy transmission, we ultimately focus on whether the overall responsiveness of credit conditions to monetary policy shocks changes in the presence of climate shocks, without attributing this change to a specific household, corporate or banking-sector mechanism.

# Data and methodology

## Data

The analysis draws on three main data sources: climate shocks, monetary policy shocks, and credit extension data. The sample covers South Africa over the period 2011–2025. All series are observed at a quarterly frequency, determined by the availability of the monetary policy shock data; higher-frequency series are aggregated to quarterly values by taking averages or sums where appropriate.

**Climate data:** Temperature and precipitation data are sourced from the ERA5 reanalysis dataset produced by the European Centre for Medium-Range Weather Forecasts^[see \url{https://cds.climate.copernicus.eu/datasets/reanalysis-era5-single-levels?tab=overview}]. ERA5 provides globally gridded, hourly atmospheric estimates at a 31 km horizontal resolution. Grid-level values are weighted by population and aggregated to monthly averages over South Africa's land area, from which we construct climate shock variables that capture deviations from long-run historical norms in temperature and precipitation.

The climate shocks are calculated as follows:

$$ ClimateShock_{t} =  \dfrac{T_{t} -\overline{T}_{t} }{\sigma(T_{t})}, $$ {#eq-weather_shock}

where $ClimateShock_{t}$ is the temperature or precipitation shock at time $t$ and $T_{t}$ is the observed population-weighted climate variable. For both temperature and precipitation, $\overline{T}_{t}$ is the calendar-month mean computed over the full sample period (e.g., the mean of all January values from 2011 to 2025), and $\sigma(T_{t})$ is the corresponding within-month standard deviation. The resulting shock series are shown in @fig-climate_shocks_data in the Appendix.

**Monetary policy data:** The monetary policy shock series is constructed using high-frequency policy surprises for South Africa from @pirozhkova2025, alongside the repurchase (repo) rate from the South African Reserve Bank (SARB). The high-frequency surprises serve as an instrument to purge the endogenous component of policy rate changes, yielding a shock series that satisfies the exogeneity requirement of the regression framework described in @sec-methodology. For robustness, we consider both market-based shocks from @pirozhkova2025 (see @fig-market_based_surprises_data) and a theory-based shock derived from the policy rate, as described in @sec-methodology below (see @fig-theory_based_surprises_data). Surprises are timed to coincide with policy rate announcement dates and aggregated to a quarterly frequency. Underlying the calculation of the are the forecasts of the real GDP growth, the policy rate (repo-rate), and the inflation rate from Bloomberg Consensus.

**Credit extension data:** Private sector credit extension data — disaggregated by borrower type (households and corporates) at the bank level — are obtained from the SARB's BA900 and BA930 bank compliance reports.^[BA930 data at the bank level are not publicly available.] These series include both credit volumes and lending rates, and are constructed following @sibande2025 and @sibande2025a by sorting and aggregating individual bank records into the broad credit categories used in the study: unsecured, secured, and mortgage credit. We use the log of credit volumes and make no other transformations to the other credit data. Summary charts are provided in @fig-lending_volume_growth_data and @fig-lending_rates. 


## Methodology {#sec-methodology}

**Structural shocks**: Rather than using the policy interest rate directly — which responds to prevailing economic conditions and is therefore endogenous — we use an unexpected change in monetary policy, commonly called a monetary policy shock, to isolate the causal effect of policy on credit markets [@miyajima2024]. We construct this shock following @merrino2022, who adapts the approach of @romer2004 to the South African context. The idea is to regress the change in the repo rate forecast on variables that policymakers were already tracking, and treat whatever is left over — the part of the rate change that cannot be explained by those forecasts — as the true policy surprise. Formally:

$$
\Delta r_t = \alpha + \tilde{r_t} + \sum_{t=0}^{2} \beta_t \Delta \tilde{y_t} + \sum_{t=0}^{2} \delta_t \tilde{\pi_t} + \varepsilon_t,
$$ {#eq-mp-shock}

where $\Delta r_t$ is the change in the repo rate forecast, $\tilde{r_t}$ is the forecasted repo rate, $\tilde{y_t}$ is the forecasted real GDP growth rate, and $\tilde{\pi_t}$ is the forecasted inflation rate. The residual $\varepsilon_t$ — the unexplained part of the forecast revision — is our monetary policy shock, $\text{MPShock}_{t}$.^[We include forecasts up to two quarters ahead to account for the common assumption among forecasters that policy is unchanged in the very near term. See @romer2004 for details.] 

As an alternative, we construct a second measure of the monetary policy surprise following @miyajima2024. This approach uses forecast errors — the gap between what forecasters expected and what actually occurred — rather than SARB forecasts. The construction proceeds in two steps. First, for each variable $i$, the forecast error is:

$$
FE^i_{t} =  EXP^i_{t} - ACT^i_{t},
$$ {#eq-forecast_error}

where $i \in \{\text{policy rate}, \text{inflation}, \text{GDP growth}\}$, $ACT^i_{t}$ is what was actually observed, and $EXP^i_{t}$ is the Bloomberg consensus forecast made beforehand. In the second step, the policy rate forecast error is regressed on the inflation and output growth forecast errors:

$$
FE^{r}_{t} = \alpha + \beta FE^{\pi}_{t} + \gamma FE^{y}_t + \epsilon_t,
$$ {#eq-m_surprise}

where $FE^{\pi}_{t}$ is the inflation forecast error and $FE^{y}_t$ is the GDP growth forecast error. The residual $\epsilon_t$ is the monetary policy surprise — the part of the policy rate miss that has nothing to do with inflation or growth news, and is therefore not anticipated by market participants.

**Market-based shocks**: As a further robustness check, we use market-based monetary policy surprises built from a high-frequency identification approach [@gurkaynak2005]. The core idea is to measure how financial market prices move in a narrow window around each MPC announcement: since little else happens in that window, any price change can be attributed to the policy news itself [@nakamura2018]. Following @pirozhkova2025, we decompose the overall surprise into four components: a target factor (the surprise in the level of the policy rate), a forward guidance factor (the surprise in the expected future path of policy), a central bank information factor (what the central bank's communication revealed about the economic outlook that markets did not already know), and a country risk factor (shifts in sovereign risk perceptions around MPC dates). Each component is used in turn as an alternative measure of $\text{MPShock}_t$ in @eq-credit and @eq-panel_credit.

**Shock purging**: Policymakers are aware of climate conditions and may already adjust rates in response to them. If so, our monetary policy shocks would partly reflect climate events rather than pure policy decisions, which would confound our estimates. To address this, we regress each monetary policy shock on the climate shock measures:

$$
\text{MPShock}^i_{t} = \text{ClimateShock}^i_t + \varepsilon^i_t,
$$ {#eq-purge}

where $\text{MPShock}^i_{t}$ is each of the monetary policy shocks described above and $\text{ClimateShock}^i_t$ are the temperature and precipitation shocks. The residual $\varepsilon^i_t$ — the part of the policy shock that cannot be explained by climate conditions — is retained as a "purged" shock. We use these purged shocks in all subsequent estimations.

** To find sources**

**Panel estimation**: Our first estimating equation tests whether the effect of a monetary policy shock on credit is amplified or dampened when a climate shock occurs at the same time:

$$
\begin{aligned}
\text{Credit}_{s,t} = &\beta_0 + \beta_1 \text{ClimateShock}_{t}^k  + \beta_2 \text{MPShock}_t + 
                       \beta_3 (\text{ClimateShock}_t^k \times \text{MPShock}_t) + \\
                       &\Gamma X_t + \gamma_s + \tau t + \varepsilon_{s,t}, 
\end{aligned}
$$ {#eq-credit}

where $\text{Credit}_{s,t}$ is credit growth for agent $s$ (households or corporates) at time $t$, and $\text{ClimateShock}_{t}^k$ captures climate shocks — temperature, precipitation, and extreme wet and dry events, indexed by $k$. The interaction term $\text{ClimateShock}_{t}^k\times\text{MPShock}_t$ is the key coefficient of interest: a significant estimate would indicate that climate shocks alter how monetary policy transmits through credit markets. $\gamma_s$ are agent fixed effects (absorbing time-invariant differences across borrower types), $\tau t$ is a linear time trend, and $\varepsilon_{s,t}$ is the error term. $X_t$ is a vector of controls added as a robustness check, including **GDP growth, the USD/ZAR exchange rate, the loan-to-deposit ratio, and the unemployment rate**.

**Panel local projections**: The panel regression above captures the contemporaneous relationship but cannot tell us how long any effect lasts. To trace the full dynamic response of credit over time, we use the local projections method of @jorda2005, estimating a separate regression for each future horizon $h = 0, 1, \ldots, H$:

$$
\begin{aligned}
{Credit}_{s,t+h} -{Credit}_{s,t-1} =  &\beta_0 + \beta_1 \text{ClimateShock}_{t}^k  + \beta_2 \text{MPShock}_t + \\ &\beta_3 (\text{ClimateShock}_t^k\times\text{MPShock}_t) + 
                                      \Gamma X_t + \gamma_s + \tau t + \varepsilon_{s,t},
\end{aligned}
$$ {#eq-panel_credit}

where $\text{Credit}_{s,t+h} - \text{Credit}_{s,t-1}$ is the cumulative change in credit growth from period $t-1$ to $t+h$, and $h$ is the horizon in quarters. Plotting the estimated $\hat{\beta}_1$, and $\hat{\beta}_2 + \hat{\beta}_3$ across horizons gives the impulse response functions, showing the differential impact of climate on credit in the quarters following a shock. All regressions use Driscoll-Kraay standard errors to account for correlation across agents and over time [@driscoll1998].

# Results

## Fixed effects


```{r}
#| label: "fig-credit_fe_temp_models"
#| fig.cap: "Interaction between climate and monetary policy shocks on lending rates"
#| fig.height: 6

fixed_effects <- read_rds(here("Outputs", "all_fe_models.rds")) 

fixed_effects |> 
  pluck(2)
```

```{=latex}
\fignote{Each point shows the estimated coefficient $\hat{\beta}_3$ on the interaction term $\text{ClimateShock} \times \text{MPShock}$ from Equation~\ref{eq-credit}, with 95\% confidence intervals. Teal points indicate statistical significance at the 5\% level; red points are insignificant. Rows correspond to individual lending rate series disaggregated by borrower type and product; columns correspond to the four monetary policy surprise measures retained after excluding the country risk and central bank information factors. All models include bank and quarter-of-year fixed effects with standard errors clustered at the bank level.}
```


## Local projections 

\newpage

```{r}
#| label: "fig-rate_corporate_temp"
#| fig.cap: "Impulse responses of corporate lending rates to monetary policy shocks: temperature shock interaction"
#| fig.height: 7
#| fig.width: 9


odd_plot_function <- function(n){
  n <- n
  (plots[[n]] + plots[[n+2]] + plots[[n+4]] ) 
}

plots <- read_rds(here("Outputs", "artifacts_lp_unsmoothed.rds")) |> 
  pluck(4)

corporate_rate_temp_gg <- odd_plot_function(n = 7) / odd_plot_function(31) / odd_plot_function(55) 

corporate_rate_temp_gg
```

```{=latex}
\fignote{Impulse response functions (IRFs) from panel local projections estimated at horizons $h = 0, \ldots, 12$ quarters following Equation~\ref{eq-panel_credit}. The blue line shows the cumulative response of the corporate lending rate to the monetary policy shock alone ($\hat{\beta}_2$); the red line shows the response when the same shock coincides with the population-weighted temperature shock ($\hat{\beta}_2 + \hat{\beta}_3$). Shaded bands are 68\% and 90\% Driscoll-Kraay confidence intervals. Rows correspond to corporate unsecured, secured, and mortgage lending rates; columns correspond to the Miyajima, Romer, and Target monetary policy surprise measures.}
```

```{r}
#| label: "fig-rate_corporate_precip"
#| fig.cap: "Impulse responses of corporate lending rates to monetary policy shocks: precipitation shock interaction"
#| fig.height: 7
#| fig.width: 9

corporate_rate_precip_gg <- odd_plot_function(n = 19) / odd_plot_function(43) / odd_plot_function(67)

corporate_rate_precip_gg

```

```{=latex}
\fignote{As Figure~\ref{fig-rate_corporate_temp} but for the population-weighted precipitation shock. The red line shows the corporate lending rate response when the monetary policy shock coincides with a precipitation shock ($\hat{\beta}_2 + \hat{\beta}_3$).}
```

\newpage

```{r}
#| label: "fig-rate_household_temp"
#| fig.cap: "Impulse responses of household lending rates to monetary policy shocks: temperature shock interaction"
#| fig.height: 7
#| fig.width: 9

household_rate_temp_gg <- odd_plot_function(n = 8) / odd_plot_function(32) / odd_plot_function(56) 

household_rate_temp_gg
```

```{=latex}
\fignote{As Figure~\ref{fig-rate_corporate_temp} but for household lending rates (unsecured, secured, and mortgage). The gap between the blue and red lines at each horizon represents the climate amplification or dampening of monetary policy transmission.}
```

```{r}
#| label: "fig-rate_household_precip"
#| fig.cap: "Impulse responses of household lending rates to monetary policy shocks: precipitation shock interaction"
#| fig.height: 7
#| fig.width: 9

household_rate_precip_gg <- odd_plot_function(n = 20) / odd_plot_function(44) / odd_plot_function(68) 

household_rate_precip_gg
```

```{=latex}
\fignote{As Figure~\ref{fig-rate_household_temp} but for the population-weighted precipitation shock. Rows correspond to household unsecured, secured, and mortgage lending rates.}
```



## Discussion

Fixed effects panel results

The contemporaneous panel estimates show that climate shocks interact with monetary policy transmission, but the evidence is uneven across shock measures and credit types. Temperature shocks produce more consistently significant interactions than precipitation shocks, with the latter yielding few panel-level estimates that clear conventional significance thresholds. The interactions are concentrated in lending rates rather than credit volumes, and within rates, corporate mortgage rates are the most responsive outcome. The Romer and Miyajima measures — once their opposing sign conventions are accounted for — tell a broadly consistent story: a temperature shock during a monetary policy tightening is associated with a dampening of the rate transmission, suggesting that climate stress blunts the pass-through of policy decisions into lending rates. The four market-based factors (target, forward guidance, CB information, country risk) are less precisely estimated in the interaction, though forward guidance and CB information still return some significant interaction coefficients for mortgage rates.

Local projections results

The local projections reveal that these effects are not merely contemporaneous but persist over the forecast horizon. Approximately 67% of interaction-horizon combinations are significant at the 68% confidence level for both temperature and precipitation shocks — a notably high share, though the 68% CI is a relatively lenient threshold common in the LP literature. The direction is predominantly dampening: across both borrower types and both credit volumes and rates, significant interactions are more often negative than positive under precipitation shocks (roughly 55–58% dampening). For temperature shocks the pattern holds for corporate borrowers and household rates, but household credit volumes show the reverse — temperature shocks appear to amplify the household credit volume response to MP, with 115 amplifying horizon-combinations against 47 dampening ones. This asymmetry between households and corporates on the volume side is the most interesting divergence between the two borrower types and warrants closer inspection.

Overall reading

Taken together, the two approaches suggest that climate shocks act primarily as a friction that weakens monetary policy pass-through, in line with the external finance premium mechanism described in the paper. Temperature shocks have more bite than precipitation shocks in the contemporaneous regression, but both climate variables produce persistent interaction effects in the LPs. The one notable exception — household credit volumes appearing to amplify under temperature shocks — could reflect a precautionary borrowing response or a compositional effect, and is worth investigating before drawing strong conclusions.

# Drivers - variation across sectors, horizons, and shock types



```{r}
#| label: "fig-asym_rate_corporate_temp"
#| fig.cap: "Asymmetric impulse responses of corporate lending rates under extreme temperature states"
#| fig.height: 7
#| fig.width: 9

asym_plot_function <- function(n){
  n <- n
  
  (asym_plots[[n]] + asym_plots[[n+1]] + asym_plots[[n+2]] ) 
}


asym_odd_function <- function(n){
  n <- n
  
  (asym_plots[[n]] + asym_plots[[n+2]] + asym_plots[[n+4]] ) 
}



asym_plots <- read_rds(here("Outputs", "artifacts_lp_unsmoothed_asym.rds")) |> 
  pluck(4)


asym_corporate_rate_temp_gg <- asym_odd_function(n = 7) / asym_odd_function(31) / asym_odd_function(55)
asym_corporate_rate_temp_gg
```

```{=latex}
\fignote{Impulse response functions from asymmetric panel local projections. The blue line shows the cumulative response of corporate lending rates to the monetary policy shock in the absence of a climate shock; the red line shows the response evaluated at an extreme positive temperature state ($+3$ SD). The gap between the two paths is the marginal climate amplification or dampening effect at that climate intensity. Shaded bands are 68\% and 90\% Driscoll-Kraay confidence intervals. Rows correspond to corporate unsecured, secured, and mortgage lending rates.}
```

```{r}
#| label: "fig-asym_rate_corporate_precip"
#| fig.cap: "Asymmetric impulse responses of corporate lending rates under extreme precipitation states"
#| fig.height: 7
#| fig.width: 9

asym_corporate_rate_precip_gg <- asym_odd_function(n = 19) / asym_odd_function(43) / asym_odd_function(67)
asym_corporate_rate_precip_gg

```

```{=latex}
\fignote{As Figure~\ref{fig-asym_rate_corporate_temp} but evaluated at an extreme negative precipitation state ($-3$ SD, i.e.\ drought conditions). A gap between the red and blue lines indicates that drought amplifies or dampens the transmission of monetary policy to corporate lending rates relative to the no-climate-shock baseline.}
```

```{r}
#| label: "fig-asym_rate_household_temp"
#| fig.cap: "Asymmetric impulse responses of household lending rates under extreme temperature states"
#| fig.height: 7
#| fig.width: 9

asym_household_rate_temp_gg <- asym_odd_function(n = 8) / asym_odd_function(32) / asym_odd_function(56)  
asym_household_rate_temp_gg
```

```{=latex}
\fignote{As Figure~\ref{fig-asym_rate_corporate_temp} but for household lending rates (unsecured, secured, and mortgage). Compares the monetary policy transmission response in the absence of a climate shock against the response under an extreme positive temperature state ($+3$ SD).}
```

```{r}
#| label: "fig-asym_rate_household_precip"
#| fig.cap: "Asymmetric impulse responses of household lending rates under extreme precipitation states"
#| fig.height: 7
#| fig.width: 9

asym_household_rate_precip_gg <- asym_odd_function(n = 20) / asym_odd_function(44) / asym_odd_function(68)
asym_household_rate_precip_gg
```

```{=latex}
\fignote{As Figure~\ref{fig-asym_rate_household_temp} but evaluated at an extreme negative precipitation state ($-3$ SD). Rows correspond to household unsecured, secured, and mortgage lending rates.}
```



```{r}
#| label: "fig-direction"
#| fig.cap: "Direction and magnitude of the climate–monetary policy interaction across credit products and shock measures"
#| fig.height: 6

extensions <- read_rds(here("Outputs", "artifacts_extensions.rds")) 
extensions |> 
  pluck("direction_gg")
```

```{=latex}
\fignote{Heatmap summarising the direction and magnitude of the climate–monetary policy interaction $\hat{\beta}_3$ from the local projections. Each cell shows the median signed interaction coefficient across all statistically significant horizons (68\% CI), with ``$+$'' indicating amplification (the climate shock strengthens monetary policy transmission) and ``$-$'' indicating dampening (the climate shock weakens transmission). Colour intensity reflects the magnitude of the median interaction, capped at $\pm 0.5$ for readability. Rows correspond to individual credit products; columns correspond to the four monetary policy surprise measures. Panels separate the results by credit type (rates vs.\ log volumes) and climate shock (temperature vs.\ precipitation).}
```

```{r}
#| label: "fig-persistence"
#| fig.cap: "Timing and persistence of the climate–monetary policy interaction"
extensions |> 
  pluck("combined_gg")

```

```{=latex}
\fignote{Distribution of two timing statistics computed from the local projection interaction coefficients. \textit{Left panel:} the horizon at which the absolute interaction effect reaches its peak, across all credit product and monetary policy shock combinations. \textit{Right panel:} the number of quarters for which the interaction coefficient is statistically significant at the 68\% confidence level (a measure of persistence). Dashed lines mark the median for each borrower group. Results are disaggregated by credit type (rates vs.\ log volumes) and climate shock (temperature vs.\ precipitation).}
```

\newpage

```{r}
#| label: "fig-product_persistence"
#| fig.cap: "Timing and persistence of the climate–monetary policy interaction by credit product"
#| fig.height: 7
extensions |> 
  pluck("combined_product_gg")

```

```{=latex}
\fignote{As Figure~\ref{fig-persistence} but disaggregated by individual credit product rather than pooled across products. Points show the median peak horizon (left panel) and median quarters significant (right panel) across all six monetary policy surprise measures, with interquartile range bars. The dashed line marks the overall median across all products and shock combinations. Corporate products are shown in dark blue; household products in red.}
```


# Conclusion

\newpage 

# References {.unnumbered}
::: {#refs}
:::


\setcounter{section}{0}
\renewcommand{\thesection}{\Alph{section}}

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}

\setcounter{figure}{0}
\renewcommand{\thefigure}{A\arabic{figure}}

\newpage

# Appendix

## Data


```{r}
#| label: fig-lending_volume_growth_data
#| fig-cap: "Private sector credit extension by borrower type and product, 2011--2025"
#| fig-height: 7
#| cache: false

lending_volume_growth_gg <- 
  read_rds(here("Outputs", "artifacts_lending_volume.rds")) |> 
  pluck(3)

lending_volume_growth_gg
```

```{=latex}
\fignote{Log of quarterly credit extension at the bank level, disaggregated by borrower type (corporate and household) and product category (unsecured, secured, and mortgage credit). Series are constructed from the South African Reserve Bank's BA900 and BA930 bank compliance reports following \citet{sibande2025} and \citet{sibande2025a}. The sample covers the period 2011Q1–2025Q1 and is restricted to the major South African banking groups.}
```


```{r}
#| label: fig-lending_rates
#| fig-cap: "Bank-level lending rates by borrower type and credit product, 2011--2025"
#| fig-height: 7
#| cache: false

lending_rates_gg <- read_rds(here("Outputs", "artifacts_lending_rates.rds")) |> 
  pluck(2)

lending_rates_gg
```

```{=latex}
\fignote{Quarterly lending rates at the bank level, disaggregated by borrower type and product (unsecured, secured, and mortgage credit for both corporates and households). Rates are expressed in percentage points and are sourced from the SARB BA930 compliance reports. Unlike credit volumes, lending rates are not log-transformed. The pronounced heterogeneity across banks and products reflects differences in risk pricing, collateral requirements, and borrower characteristics.}
```


```{r}
#| label: fig-climate_shocks_data
#| fig-cap: "Population-weighted temperature and precipitation shocks for South Africa, 2011--2025"
#| fig-height: 2
#| cache: false

climate_shocks_gg <- read_rds(here("Outputs", "artifacts_climate_shocks.rds")) |> 
  pluck(2)

climate_shocks_gg
```

```{=latex}
\fignote{Standardised climate shock series constructed from ERA5 reanalysis data (European Centre for Medium-Range Weather Forecasts) at a 31\,km horizontal resolution. Each observation is the deviation of the population-weighted monthly average from the long-run calendar-month mean, expressed in standard deviation units: $\text{ClimateShock}_t = (T_t - \bar{T}_t)/\sigma(T_t)$. Positive values indicate warmer or wetter conditions than the historical norm; negative values indicate cooler or drier conditions. Grid-level values are weighted by population density and aggregated to a quarterly frequency by averaging within-quarter monthly values.}
```


```{r}
#| label: fig-market_based_surprises_data
#| fig-cap: "High-frequency market-based monetary policy surprise factors, 2011--2025"
#| cache: false
#| fig.height: 2

market_based_surprises_gg <- read_rds(here("Outputs", "artifacts_market_based_surprises.rds")) |> 
  pluck(2)

market_based_surprises_gg
```

```{=latex}
\fignote{Monetary policy surprise factors derived from the high-frequency identification approach of \citet{gurkaynak2005} and constructed for South Africa by \citet{pirozhkova2025}. Each factor is extracted from movements in financial market prices in a narrow window around Monetary Policy Committee (MPC) announcement dates. Four components are shown: the \textit{target factor} (surprise in the level of the policy rate), the \textit{forward guidance factor} (surprise in the expected future path of policy), the \textit{central bank information factor} (economic outlook news revealed by the central bank's communication), and the \textit{country risk factor} (shifts in sovereign risk perceptions around MPC dates). Series are aggregated to a quarterly frequency.}
```

```{r}
#| label: fig-theory_based_surprises_data
#| fig-cap: "Theory-based monetary policy surprises: Romer--Romer and Miyajima measures, 2011--2025"
#| fig.height: 2
#| cache: false

theory_based_surprises_gg <- read_rds(here("Outputs", "artifacts_surprises.rds")) |> 
  pluck(3, 3)

theory_based_surprises_gg
```

```{=latex}
\fignote{Two theory-based monetary policy surprise measures used as alternative identification strategies. The \textit{Romer measure} (blue) is the residual from regressing the change in the SARB's repo rate forecast on its own internal projections for GDP growth and inflation, following the approach of \citet{romer2004} adapted to South Africa by \citet{merrino2022}; a positive value indicates an unexpected tightening relative to the SARB's own information set. The \textit{Miyajima measure} (red) is the residual from regressing the Bloomberg consensus forecast error for the policy rate on forecast errors for inflation and GDP growth \citep{miyajima2024}; a positive value indicates the repo rate came in above what economic news alone would have predicted. Both series are aggregated to a quarterly frequency and purged of climate shock variation prior to use in the main regressions (see Equation~\ref{eq-purge}).}
```


## Descriptive Statistics


```{r}
#| label: tbl-descriptives
#| tbl-cap: "Summary statistics for key variables used in the analysis"
#| ft.arraystretch: 0.4


descriptives_table <- 
  read_rds(here("Outputs", "artifacts_descriptive_statistics.rds")) |> 
  pluck(1) |> 
  filter(
    !credit_category %in% c("forward_guidance", "central_bank_information", "country_risk")
  ) |> 
   mutate(
    credit_category = str_replace_all(credit_category, "pop", "Population"),
    credit_category = str_replace_all(credit_category, "temp", "Temperature"),
    credit_category = str_replace_all(credit_category, "precip", "Precipitation")
  ) |> 
  mutate(credit_category = credit_category |> str_replace_all("_", " ") |> str_to_title()) |> 
  flextable::as_grouped_data(groups = "groups") |> 
  flextable() |> 
  colformat_double(digits = 2) |>
  width(j = "credit_category", width = 1.2) |>
  width(j = "credit_category", width = 1.5) |>
  width(j = c("mean", "median", "sd", "min", "max"), width = 0.6) |>
  width(j = "n", width = 0.5) |> 
  set_header_labels(groups = "", credit_category = "Variable",
                    mean = "Mean", median = "Median", sd = "SD",
                    min = "Min", max = "Max", n = "N") 
 
  
descriptives_table

```

```{=latex}
\fignote{Summary statistics computed over the full estimation sample (2011Q1--2025Q1) at the bank-quarter level. Credit volumes are expressed in log terms; lending rates are in percentage points; climate shocks are standardised deviations from the long-run calendar-month mean (see Equation~\ref{eq-weather_shock}); and monetary policy surprises are expressed in percentage points. The country risk factor, forward guidance factor, and central bank information factor are excluded from this table to preserve space but are included in the main regressions. $N$ denotes the number of non-missing bank-quarter observations.}
```


<!-- ## Sector Credit Exposure  -->

```{r}
#| label: fig-sector_credit_exposure
#| fig-cap: "Sector credit exposure"
#| fig.height: 7
#| cache: false
#| eval: false
#| include: false


sector_credit_exposure_gg <- 
  read_rds(here("Outputs", "artifacts_sector_credit_exposure.rds")) |> 
  pluck(2)

sector_credit_exposure_gg
```

<!-- # Detailed results -->

```{r}
#| label: "fixed_effects_temp"
#| tbl-cap: "Estimated coefficients from the fixed effects models: Temperature shock"
#| ftarraystrech: 0
#| eval: false
#| include: false

shock_models_tbl <- read_rds(here("Outputs", "all_fe_models.rds")) |> 
  pluck(1) 

shock_models_tbl |> 
  filter(climate_shock == "pop_temp_shock") |> 
  select(-climate_shock, -`(Intercept)`) |> 
  mutate(
    Type = if_else(str_detect(dependant, "_rate"), "Lending Rates", "Credit Growth")
  ) |>
  arrange(
    Type,
    dependant,
    case_when(
      str_detect(MPShock, "miyajima")     ~ 1,
      str_detect(MPShock, "romer")        ~ 2,
      str_detect(MPShock, "target")       ~ 3,
      str_detect(MPShock, "forward")      ~ 4,
      str_detect(MPShock, "central_bank") ~ 5,
      str_detect(MPShock, "country_risk") ~ 6,
      .default = 7
    )
  ) |> 
  mutate(surprises = str_replace_all(surprises, 
                                   c("miyajima_surprise_pop_precip_shock_resid" = "Miyajima",
                                     "miyajima_surprise_pop_temp_shock_resid" = "Miyajima",
                                     "romer_surprise_pop_precip_shock_resid" = "Romer",
                                     "romer_surprise_pop_temp_shock_resid" = "Romer",
                                     "target_pop_precip_shock_resid" = "Target",
                                     "target_pop_temp_shock_resid" = "Target",
                                     "forward_guidance_pop_precip_shock_resid" = "Forward guidance",
                                     "forward_guidance_pop_temp_shock_resid" = "Forward guidance",
                                     "central_bank_information_pop_precip_shock_resid" = "Central bank information",
                                     "central_bank_information_pop_temp_shock_resid" = "Central bank information",
                                     "country_risk_pop_precip_shock_resid" = "Country risk",
                                     "country_risk_pop_temp_shock_resid" = "Country risk"
                                     ))) |> 
  mutate(dependant = str_replace_all(dependant, c(
                                          "corporate_secured_credit" = "Corporate secured",
                                          "corporate_unsecured_credit" = "Corporate unsecured",
                                          "corporate_mortgage" = "Corporate mortgage",
                                          "household_secured_credit" = "Household secured",
                                          "household_unsecured_credit" = "Household unsecured",
                                          "household_mortgages" = "Household mortgages",
                                          "Corporate secured_rate" = "Corporate secured",
                                          "Corporate unsecured_rate" = "Corporate unsecured",
                                          "Corporate mortgage_rate" = "Corporate mortgage",
                                          "Household secured_rate" = "Household secured",
                                          "Household unsecured_rate" = "Household unsecured",
                                          "household_mortgage_rate" = "Household mortgages"
                                          ))) |> 
  as_grouped_data(groups = c("Type"), expand_single = TRUE) |>
  flextable() |>
  merge_v(j = "Type") |>
  merge_v(j = "dependant") |>
  set_header_labels(Type = "", dependant = "", surprises = "") |>
  set_table_properties(layout = "fixed") |>
  fontsize(size = 5, part = "all") |> 
  autofit(add_w = .2)
```

<!-- ```{=latex} -->
<!-- {\footnotesize -->
<!-- \noindent \textit{Note:}  All models include bank fixed effects. Standard errors are clustered at the bank level. -->

<!-- \noindent $^{*}$\(p < 0.10\), $^{**}$\(p < 0.05\), $^{***}$\(p < 0.01\) -->
<!-- } -->

<!-- ``` -->



```{r}
#| label: "fixed_effects_precip"
#| tbl-cap: "Estimated coefficients from the fixed effects models: Precipitation shock"
#| ftarraystrech: 0
#| eval: false
#| include: false

shock_models_tbl <- fixed_effects |> 
  pluck(1) 

shock_models_tbl |> 
  filter(climate_shock == "pop_precip_shock") |> 
  select(-climate_shock, -`(Intercept)`) |> 
  mutate(
    Type = if_else(str_detect(dependant, "_rate"), "Lending Rates", "Credit Growth")
  ) |>
  arrange(
    Type,
    dependant,
    case_when(
      str_detect(MPShock, "miyajima")     ~ 1,
      str_detect(MPShock, "romer")        ~ 2,
      str_detect(MPShock, "target")       ~ 3,
      str_detect(MPShock, "forward")      ~ 4,
      str_detect(MPShock, "central_bank") ~ 5,
      str_detect(MPShock, "country_risk") ~ 6,
      .default = 7
    )
  ) |> 
  mutate(surprises = str_replace_all(surprises, 
                                   c("miyajima_surprise_pop_precip_shock_resid" = "Miyajima",
                                     "miyajima_surprise_pop_temp_shock_resid" = "Miyajima",
                                     "romer_surprise_pop_precip_shock_resid" = "Romer",
                                     "romer_surprise_pop_temp_shock_resid" = "Romer",
                                     "target_pop_precip_shock_resid" = "Target",
                                     "target_pop_temp_shock_resid" = "Target",
                                     "forward_guidance_pop_precip_shock_resid" = "Forward guidance",
                                     "forward_guidance_pop_temp_shock_resid" = "Forward guidance",
                                     "central_bank_information_pop_precip_shock_resid" = "Central bank information",
                                     "central_bank_information_pop_temp_shock_resid" = "Central bank information",
                                     "country_risk_pop_precip_shock_resid" = "Country risk",
                                     "country_risk_pop_temp_shock_resid" = "Country risk"
                                     ))) |> 
  mutate(dependant = str_replace_all(dependant, c(
                                          "corporate_secured_credit" = "Corporate secured",
                                          "corporate_unsecured_credit" = "Corporate unsecured",
                                          "corporate_mortgage" = "Corporate mortgage",
                                          "household_secured_credit" = "Household secured",
                                          "household_unsecured_credit" = "Household unsecured",
                                          "household_mortgages" = "Household mortgages",
                                          "Corporate secured_rate" = "Corporate secured",
                                          "Corporate unsecured_rate" = "Corporate unsecured",
                                          "Corporate mortgage_rate" = "Corporate mortgage",
                                          "Household secured_rate" = "Household secured",
                                          "Household unsecured_rate" = "Household unsecured",
                                          "household_mortgage_rate" = "Household mortgages"
                                          ))) |> 
  as_grouped_data(groups = c("Type"), expand_single = TRUE) |>
  flextable() |>
  merge_v(j = "Type") |>
  merge_v(j = "dependant") |>
  set_header_labels(Type = "", dependant = "", surprises = "") |>
  set_table_properties(layout = "fixed") |>
  fontsize(size = 5, part = "all") |> 
  autofit(add_w = .2)
```


<!-- ```{=latex} -->
<!-- {\footnotesize -->
<!-- \noindent \textit{Note:}  All models include bank fixed effects. Standard errors are clustered at the bank level. -->

<!-- \noindent $^{*}$\(p < 0.10\), $^{**}$\(p < 0.05\), $^{***}$\(p < 0.01\) -->
<!-- } -->

<!-- ``` -->

# Credit growth results

## Fixed effects

```{r}
#| label: "fig-rates_fe_temp_models"
#| fig.cap: "Interaction between climate and monetary policy shocks on credit growth: fixed effects estimates"
#| fig.height: 6

fixed_effects |> 
  pluck(3)
```

```{=latex}
\fignote{Each point shows the estimated coefficient $\hat{\beta}_3$ on the interaction term $\text{ClimateShock} \times \text{MPShock}$ from Equation~\ref{eq-credit}, with 95\% confidence intervals. Teal points indicate statistical significance at the 5\% level; red points are insignificant. Rows correspond to individual log credit volume series disaggregated by borrower type and product; columns correspond to the four monetary policy surprise measures retained after excluding the country risk and central bank information factors. All models include bank and quarter-of-year fixed effects with standard errors clustered at the bank level. Credit volumes are expressed in logarithms so coefficients represent proportional responses.}
```


## Local projections


```{r}
#| label: "fig-corporate_temp"
#| fig.cap: "Impulse responses of corporate credit growth to monetary policy shocks: temperature shock interaction"
#| fig.height: 7
#| fig.width: 9


plot_function <- function(n){
  n <- n
  
  (plots[[n]] + plots[[n+1]] + plots[[n+2]] ) 
}



corporate_temp_gg <- plot_function(n = 1) / plot_function(25) /  plot_function(49)

corporate_temp_gg
```

```{=latex}
\fignote{Impulse response functions (IRFs) from panel local projections estimated at horizons $h = 0, \ldots, 12$ quarters following Equation~\ref{eq-panel_credit}. The blue line shows the cumulative response of log corporate credit growth to the monetary policy shock alone ($\hat{\beta}_2$); the red line shows the response when the same shock coincides with the population-weighted temperature shock ($\hat{\beta}_2 + \hat{\beta}_3$). Shaded bands are 68\% and 90\% Driscoll-Kraay confidence intervals. Rows correspond to corporate unsecured, secured, and mortgage credit; columns correspond to the Miyajima, Romer, and Target monetary policy surprise measures.}
```

```{r}
#| label: "fig-corporate_precip"
#| fig.cap: "Impulse responses of corporate credit growth to monetary policy shocks: precipitation shock interaction"
#| fig.height: 7
#| fig.width: 9

corporate_precip_gg <- plot_function(13) / plot_function(37) /  plot_function(61) 
corporate_precip_gg

```

```{=latex}
\fignote{As Figure~\ref{fig-corporate_temp} but for the population-weighted precipitation shock. The red line shows the corporate credit growth response when the monetary policy shock coincides with a precipitation shock ($\hat{\beta}_2 + \hat{\beta}_3$). Rows correspond to corporate unsecured, secured, and mortgage credit.}
```

\newpage

```{r}
#| label: "fig-household_temp"
#| fig.cap: "Impulse responses of household credit growth to monetary policy shocks: temperature shock interaction"
#| fig.height: 7
#| fig.width: 9

household_temp_gg <- plot_function(n = 4) / plot_function(28) / plot_function(52) 

household_temp_gg
```

```{=latex}
\fignote{As Figure~\ref{fig-corporate_temp} but for household credit growth (unsecured, secured, and mortgage). The gap between the blue and red lines at each horizon represents the marginal effect of the temperature shock on the transmission of monetary policy to household credit volumes.}
```

```{r}
#| label: "fig-household_precip"
#| fig.cap: "Impulse responses of household credit growth to monetary policy shocks: precipitation shock interaction"
#| fig.height: 7
#| fig.width: 9

household_precip_gg <- plot_function(n = 16) / plot_function(40) / plot_function(64) 
household_precip_gg
```

```{=latex}
\fignote{As Figure~\ref{fig-household_temp} but for the population-weighted precipitation shock. Rows correspond to household unsecured, secured, and mortgage credit growth.}
```


## Asymmetric local projections


```{r}
#| label: "fig-asym_corporate_temp"
#| fig.cap: "Asymmetric impulse responses of corporate credit growth under extreme temperature states"
#| fig.height: 7
#| fig.width: 9

asym_corporate_temp_gg <- asym_plot_function(n = 1) / asym_plot_function(25) /  asym_plot_function(49)  

asym_corporate_temp_gg
```

```{=latex}
\fignote{Impulse response functions from asymmetric panel local projections. The blue line shows the cumulative response of log corporate credit growth to the monetary policy shock in the absence of a climate shock; the red line shows the response evaluated at an extreme positive temperature state ($+3$ SD). The gap between the two paths is the marginal climate amplification or dampening effect at that climate intensity. Shaded bands are 68\% and 90\% Driscoll-Kraay confidence intervals. Rows correspond to corporate unsecured, secured, and mortgage credit growth.}
```

```{r}
#| label: "fig-asym_corporate_precip"
#| fig.cap: "Asymmetric impulse responses of corporate credit growth under extreme precipitation states"
#| fig.height: 7
#| fig.width: 9

asym_corporate_precip_gg <- asym_plot_function(13) / asym_plot_function(37) /  asym_plot_function(61) 
asym_corporate_precip_gg

```

```{=latex}
\fignote{As Figure~\ref{fig-asym_corporate_temp} but evaluated at an extreme negative precipitation state ($-3$ SD, i.e.\ drought conditions). A divergence between the red and blue lines indicates that drought conditions amplify or dampen the transmission of monetary policy to corporate credit volumes relative to the no-climate-shock baseline. Rows correspond to corporate unsecured, secured, and mortgage credit growth.}
```

\newpage

```{r}
#| label: "fig-asym_household_temp"
#| fig.cap: "Asymmetric impulse responses of household credit growth under extreme temperature states"
#| fig.height: 7
#| fig.width: 9

asym_household_temp_gg <- asym_plot_function(n = 4) / asym_plot_function(28) / asym_plot_function(52)
asym_household_temp_gg
```

```{=latex}
\fignote{As Figure~\ref{fig-asym_corporate_temp} but for household credit growth (unsecured, secured, and mortgage). Compares the monetary policy transmission response in the absence of a climate shock against the response under an extreme positive temperature state ($+3$ SD).}
```

```{r}
#| label: "fig-asym_household_precip"
#| fig.cap: "Asymmetric impulse responses of household credit growth under extreme precipitation states"
#| fig.height: 7
#| fig.width: 9



asym_household_precip_gg <- asym_odd_function(n = 20) / asym_odd_function(44) / asym_odd_function(68)
asym_household_precip_gg
```

```{=latex}
\fignote{As Figure~\ref{fig-asym_household_temp} but evaluated at an extreme negative precipitation state ($-3$ SD). Rows correspond to household unsecured, secured, and mortgage credit growth.}
```


\newpage

# Credit rates results with controls (to complete)



